Generating exact lattices in a WFST framework

### 2011-09-28 misc/papers/icassp12_lat/paper.tex
Fixes to paper.
git-svn-id: https://svn.code.sf.net/p/kaldi/code/trunk@530 5e6a8d80-dfce-4ca6-a32a-6e07a63d50c8

\name{ \em Daniel Povey$^1$, Mirko Hannemann$^{1,2}$,  \\
  \em {Gilles Boulianne}$^3$, {Luk\'{a}\v{s} Burget}$^4$, {Arnab Ghoshal}$^5$, {Milos Janda}$^2$, {Stefan Kombrink}$^2$, \\
  \em {Petr Motl\'{i}\v{c}ek}$^6$, {Yanmin Qian}$^7$, {Ngoc Thang Vu}$^8$, {Korbinian Riedhammer}$^9$, {Karel Vesel\'{y}}$^2$
    \thanks{Thanks to Sanjeev Khudanpur for his help in preparing the paper}}

@@

The graph creation process we use in our toolkit, Kaldi~\cite{kaldi_paper},
is very close to the standard recipe described in~\cite{wfst},
where the Weighted Finite State Transducer (WFST) decoding graph is
\begin{equation}
  \HCLG = \min(\det(H \circ C \circ L \circ G)),
\end{equation}
where $\circ$ is WFST composisition (note: view $\HCLG$ as a single symbol).
For concreteness we will speak of ``costs'' rather
than weights, where a cost is a floating point number that typically represents a negated
log-probability.  A WFST has a set of states with one distinguished
start state\footnote{This is the formulation that corresponds best with the toolkit we use.},
each state has a final-cost (or $\infty$ for non-final states);
and there is a set of arcs, where each arc has a weight,
weight (just think of this as a cost for now), an input label and an output
label.  In $\HCLG$, the input labels are the identifiers of context-dependent
HMM states, and the output labels represent words.  For both the input and output
symbols, the special label $\epsilon$ may appear meaning ``no label is present.''

@@

We now summarize the lattice generation algorithm.  During decoding, we create a data-structure
corresponding to a full state-level lattice.  That is, for every arc of $\HCLG$ we traverse
on every frame, we create a separate arc in the state-level lattice.  These arcs
contain the acoustic and graph costs separately.  We prune the state-level graph using
a beam $\alpha$; we do this periodically (every 25 frames) but this is equivalent to
doing it just once at the end (similar to~\cite{efficient_general}).  Let the pruned
state-level lattice that we get after pruning it at the end of the utterance be $P$.

Let $Q = \inv(P)$, and let $E$ be an encoded version of $Q$ as described above (with the
state labels as part of the weights).  The final lattice we output is
\begin{equation}
   L = \mathrm{prune}(\mathrm{det}(\mathrm{rmeps}(E)), \alpha) .
\end{equation}
The determinization and epsilon removal are done together by a single algorithm
that we will describe below.

The resulting lattice $L$ is a deterministic, acyclic weighted acceptor with the 
words as the labels, and the graph and acoustic costs and the alignments
encoded into the weights.  The costs and alignments are not ``synchronized'' 
with the words.

@@

We report experimental results on the Wall Street Journal database of
read speech.  
Our system is a standard mixture-of-Gaussians system trained on the SI-284
training data; we test on the November 1992 evaluation data.  
For these experiments we generate lattices with the bigram language model
supplied with the WSJ database, and for rescoring experiments we
use the trigram language model.  The acoustic scale was $1/16$ for first-pass
decoding and $1/15$ for LM rescoring.

For simplicity, our results were all obtained using a decoder that
does not support a ``maximum active states'' option, so the only variables
to consider are the beam used in the Viterbi beam search, and the separate
beam $\alpha$ used for lattice generation.

@@

Figure~\ref{fig:latbeam} shows how various quantities change as we vary
$\alpha$, with the Viterbi beam fixed at 15.  Note that we get all the improvement from
LM rescoring by increasing $\alpha$ to 4.  The time taken by our algorithm started to increase rapidly after about
$\alpha=8$, so a value of $\alpha$ anywhere between about 4 and 8 is sufficient for LM rescoring 
and still does not slow down decoding too much.
Note that out of vocabularly words (OOVs) provide a floor on the lattice oracle error rate.
Of the 333 test utterances, 87 contained an OOV word, yet only 93 sentences had oracle errors
with $\alpha=10$.  Figure~\ref{fig:viterbibeam} shows the effect of varying the
Viterbi decoding beam, while leaving $\alpha$ fixed at 7.

>>>>

\name{ \em Daniel Povey$^1$, Mirko Hannemann$^{1,2}$,  \\
  \em {Gilles Boulianne}$^3$, {Luk\'{a}\v{s} Burget}$^4$, {Arnab Ghoshal}$^5$, {Milos Janda}$^2$, {Stefan Kombrink}$^2$, \\
  \em {Petr Motl\'{i}\v{c}ek}$^6$, {Yanmin Qian}$^7$, {Ngoc Thang Vu}$^8$, {Korbinian Riedhammer}$^9$, {Karel Vesel\'{y}}$^2$
    \thanks{Thanks to Sanjeev Khudanpur for his help in preparing the paper, and to Honza Cernocky, Renata Kohlova, Martin Karafiat and Tomas Mikolov for their help relating to the Kaldi'11 workshop at BUT.}}

@@

The graph creation process we use in our toolkit, Kaldi~\cite{kaldi_paper},
is very close to the standard recipe described in~\cite{wfst},
where the Weighted Finite State Transducer (WFST) decoding graph is
\begin{equation}
  \HCLG = \min(\det(H \circ C \circ L \circ G)),
\end{equation}
where $\circ$ is WFST composition (note: view $\HCLG$ as a single symbol).
For concreteness we will speak of ``costs'' rather
than weights, where a cost is a floating point number that typically represents a negated
log-probability.  A WFST has a set of states with one distinguished
start state\footnote{This is the formulation that corresponds best with the toolkit we use.},
each state has a final-cost (or $\infty$ for non-final states);
and there is a set of arcs, where each arc has a weight
(just think of this as a cost for now), an input label and an output
label.  In $\HCLG$, the input labels are the identifiers of context-dependent
HMM states, and the output labels represent words.  For both the input and output
symbols, the special label $\epsilon$ may appear meaning ``no label is present.''

@@

We now summarize the lattice generation algorithm.  During decoding, we create a data-structure
corresponding to a full state-level lattice.  That is, for every arc of $\HCLG$ we traverse
on every frame, we create a separate arc in the state-level lattice.  These arcs
contain the acoustic and graph costs separately.  We prune the state-level graph using
a beam $\alpha$; we do this periodically (every 25 frames) but this is equivalent to
doing it just once at the end, as in~\cite{efficient_general}.  Let the 
final pruned state-level lattice be $P$.

Let $Q = \inv(P)$, and let $E$ be an encoded version of $Q$ as described above (with the
state labels as part of the weights).  The final lattice is
\begin{equation}
   L = \mathrm{prune}(\mathrm{det}(\mathrm{rmeps}(E)), \alpha) .
\end{equation}
The determinization and epsilon removal are done together by a single algorithm
that we will describe below.  $L$ is a deterministic, acyclic weighted acceptor with the 
words as the labels, and the graph and acoustic costs and the alignments
encoded into the weights.  The costs and alignments are not ``synchronized'' 
with the words.

@@

We report experimental results on the Wall Street Journal database of
read speech.  
Our system is a standard mixture-of-Gaussians system trained on the SI-284
training data; we test on the November 1992 evaluation data.  
For these experiments we generate lattices with the bigram language model
supplied with the WSJ database, and for rescoring experiments we
use the trigram language model.  The acoustic scale was $1/16$ for first-pass
decoding and $1/15$ for LM rescoring.  
For simplicity we used a decoder that
does not support a ``maximum active states'' option, so the only variables
to consider are the beam used in the Viterbi beam search, and the separate
beam $\alpha$ used for lattice generation.

@@

Figure~\ref{fig:latbeam} shows how various quantities change as we vary
$\alpha$, with the Viterbi beam fixed at 15.  Note that we get all the improvement from
LM rescoring by increasing $\alpha$ to 4.  The time taken by our algorithm started to increase rapidly after about
$\alpha=8$, so a value of $\alpha$ anywhere between about 4 and 8 is sufficient for LM rescoring 
and still does not slow down decoding too much.
Out of vocabularly words (OOVs) provide a floor on the lattice oracle error rate:
of 333 test utterances, 87 contained at least one OOV word, yet only 93 sentences (6 more) had oracle errors
with $\alpha=10$.  Lattice density is defined as the average number of arcs crossing each frame.
Figure~\ref{fig:viterbibeam} shows the effect of varying the
Viterbi decoding beam, while leaving $\alpha$ fixed at 7.
